---
title: "Sector Distributions"
output: html_notebook
---

In this document, I will look at the distribution of gammas within nonprofit sectors in the 31 eastern states of the US.

```{r}
load("~/Documents/Coe College/Spellman 2018/RData/NTEECCzip.Rdata")
load("~/Documents/Coe College/Spellman 2018/RData/NTEE1zip.Rdata")
load("~/Documents/Coe College/Spellman 2018/RData/East15.Rdata")
```

Using East15, I need to create columns in the NTEECC and NTEE1 Rdata files containing the NTEE1 group and/or the NTMAJ12 sector.

```{r}
sectors <- aggregate(East15$TOTREV,
                       list(East15$NTEECC, East15$NTEE1, East15$NTMAJ12),
                       sum)
colnames(sectors) <- c("Corecode", "Group", "Sector", "Revenue")
levels(sectors$Sector)
#Creating another column with better names for sectors by first making a dataframe and then merging.
s <- data.frame("Sector"=c("AR", "BH", "ED", "EH", "EN", "HE", "HU", "IN", "MU", "PU", "RE", "UN"), "Name"= c("Arts and Humanities", "Higher Education", "Education", "Hospitals", "Environment", "Health", "Human Services", "International", "Mutual Benefit", "Public and Societal Benefit", "Religious", "Unknown"))

#Now adding these columns to the data files with the gamma values. I don't need revenue, I just used it to get the other three columns.
NTEECCzip$Group <- sectors$Group[ match(NTEECCzip$Industry, sectors$Corecode)]
NTEECCzip$Sector <- sectors$Sector[ match(NTEECCzip$Industry, sectors$Corecode)]
NTEECCzip$Name <- s$Name[ match(NTEECCzip$Sector, s$Sector)]
```
In order to do the same to the NTEE1 dataframe, I first need to figure out if the use of NTMAJ 12 rather than NTMAJ 10 affected the gamma for Groups B and E, which are the only ones affected by the NTMAJ12 classification. I will save that task for later and concentrate on looking at the distributions of gammas among sectors for core codes.

```{r}
library(ggplot2)
ggplot(NTEECCzip, aes(x=gamma)) + 
  geom_histogram(data=subset(NTEECCzip, NTEECCzip$gamma>0), fill = "green") +
  geom_histogram(data=subset(NTEECCzip, NTEECCzip$gamma<=0), fill = "red") +
  facet_wrap( ~ Name, ncol=2, scales = "free")
ggsave("Sector Dists/Output/histograms.jpg", width=16, height=20)


ggplot(NTEECCzip, aes(x=NTEECCzip$gamma)) + 
  geom_histogram() +
  facet_wrap( ~ Name, ncol=2, scales = "free")
ggsave("Sector Dists/Output/histo2.jpg", width=16, height=20)

```

I'm getting slight differences between the two sets of histograms, which shouldn't be the case. I'm going to see if the aes part of the code makes a difference.

```{r}
ggplot(NTEECCzip, aes(x=gamma))+
  geom_histogram() +
  xlim(c(-.01, .01))

ggplot(NTEECCzip, aes(x=gamma))+
  geom_histogram(data=subset(NTEECCzip, NTEECCzip$gamma>0), fill = "green") +
  geom_histogram(data=subset(NTEECCzip, NTEECCzip$gamma<=0), fill = "red") +
  xlim(c(-.01, .01))



```
 The difference is here, too, and I'm not sure what causes it. However, both graphics seem accurate although they are scaled a little differently...
 